Metadata and Other Structures in texor

### 2023-08-19 supplement/metadata/metadata.tex
Updated supplementary materials
edits to metadata supplement

\section{Introduction}
There is a difference in the structure of metadata and generally Rmarkdown has more
meta-data entries than its LaTeX counterpart. So for the conversion, main task is to 
transform the meta data and include it in the generated Rmarkdown file, matching the
LaTeX data as closely as possible.

Pandoc when used with \verb|-s| or \verb|standalone| mode reads out some of the existing
meta data. The extracted author meta-data are listed below:

\subsubsection{Metadata Read from LaTeX file}

\begin{itemize}
  \item Author Names 
  \item Author address(affiliation)
  \item ORCID number
  \item Title
  \item Bibliography
  \item Abstract
  \item CRAN/BIO packages
\end{itemize}

@@

\subsubsection{Metadata Read from DESCRIPTION file}

\begin{itemize}
  \item Date
  \item Slug
  \item Volume and Issue
\end{itemize}

Some details like the Volume and Issue were picked up from folder structure as well
in some legacy articles where DESCRIPTION file was not available.

@@

\begin{table}[htbp]
\centering
\begin{tabular}{| c | c |}
 \hline
 Command & Render \\
 \hline
 \verb|\acronym{A}| & \acronym{A} \\ \hline
\verb|\R| & \R  \\ \hline
 \verb|\pkg{texor}|& \pkg{texor} \\ \hline
 \verb|\CRANpkg{texor}|& \CRANpkg{texor} \\ \hline
 \verb|\BIOpkg{Biobase}|      & \BIOpkg{Biobase}  \\ \hline
 \verb|\ctv{ReproducibleResearch}| & \ctv{ReproducibleResearch}  \\ \hline
\verb|\command{help}| & \command{help} \\
\hline
\end{tabular}
\caption{Other commands supported by \CRANpkg{texor} and Pandoc}
\label{table:1}
\end{table}

@@

Table \ref{table:2} represents all the ways one can use citations in LaTeX and
expect the generated output.

\begin{table}[htbp]
\centering
\begin{tabular}{| c | c |}
 \hline
 Command & Render \\
 \hline
 \verb|\citet{pandoc}| & \citet{pandoc} \\ \hline
\verb|\citep{pandoc}| & \citep{pandoc} \\ \hline
 \verb|\citet*{pandoc}| & \citet*{pandoc} \\ \hline
\verb|\citep*{pandoc}| & \citep*{pandoc} \\ \hline
 \verb|\citeyear{pandoc}| & \citeyear{pandoc} \\ \hline
\verb|\citeauthor{pandoc}| & \citeauthor{pandoc} \\ \hline
 \verb|\cite{pandoc}| & \cite{pandoc} \\ \hline
\end{tabular}
\caption{Different citations in LaTeX}
\label{table:2}
\end{table}

\subsubsection{Footnotes}
\begin{table}[htbp]
\centering
\begin{tabular}{| c | c |}
 \hline
 Command & Render \\
 \hline
 \verb|\acronym{A}\footnote{This works in Web article}| & \acronym{A}\footnote{This works in Web article} \\ \hline
\verb|\R\footnote[21]{Its 2 not 21 :(}| & \R\footnote[21]{Its 2 not 21 :(}  \\ \hline
\end{tabular}
\caption{Demo of footnotes}
\label{table:3}
\end{table}

Footnotes do not work in \verb|tabular| environment in LaTeX but it does work in Rmarkdown\footnote{This works in LaTeX and  Web article}.
Custom Footnote number works in LaTeX but does not work in web articles\footnote[21]{Forever 21 :)}.

\subsubsection{BlockQuotes}
\begin{quote}
This BlockQuote should Justify an example.
\end{quote}

\subsubsection{Links}
Most links work just fine using \verb|\href| and \verb|\url| command will work flawlessly.
\begin{table}[htbp]
\centering
\begin{tabular}{| c | c |}
 \hline
 Command & Render \\
 \hline
 \verb|\href{www.google.com}{Google}| & \href{www.google.com}{Google} \\ \hline
\verb|\url{www.google.com}| & \url{www.google.com}  \\ \hline
\verb|Table \ref{table:3}| & Table \ref{table:3}  \\ \hline
\end{tabular}
\caption{Links}
\label{table:4}
\end{table}

\section{Summary}
In summary the \CRANpkg{texor} package alongside pandoc supports:
\begin{itemize}
\item Extracting Metadata and putting it together well.
\item Handling Links, BlockQuotes, Citations and Footnotes.
\end{itemize}

>>>>

\section{Introduction}
There is a difference in the structure of metadata and generally R Markdown has more
metadata entries than its LaTeX counterpart. So for the conversion, the main task is to 
transform the metadata and include it in the generated R Markdown file, matching the
LaTeX metadata as closely as possible.

When used with the \verb|-s| or \verb|standalone| mode, pandoc reads out some of the existing
meta data. The extracted metadata are listed below.

\subsubsection{Metadata read from LaTeX file}

\begin{itemize}
  \item Author names 
  \item Author address (affiliation)
  \item ORCID number
  \item Title
  \item Bibliography
  \item Abstract
  \item CRAN/Bioconductor packages
\end{itemize}

@@

\subsubsection{Metadata read from DESCRIPTION file}

\begin{itemize}
  \item Date
  \item Slug
  \item Volume and issue
\end{itemize}

Some metadata like the volume and issue were picked up from the folder structure for some legacy articles, where the DESCRIPTION file was not available.

@@

\begin{table}[htbp]
\centering
\begin{tabular}{| c | c |}
 \hline
 Command & Render \\
 \hline
 \verb|\acronym{A}| & \acronym{A} \\ \hline
\verb|\R| & \R  \\ \hline
 \verb|\pkg{texor}|& \pkg{texor} \\ \hline
 \verb|\CRANpkg{texor}|& \CRANpkg{texor} \\ \hline
 \verb|\BIOpkg{Biobase}|      & \BIOpkg{Biobase}  \\ \hline
 \verb|\ctv{ReproducibleResearch}| & \ctv{ReproducibleResearch}  \\ \hline
\verb|\command{help}| & \command{help} \\
\hline
\end{tabular}
\caption{Other commands supported by \CRANpkg{texor} and pandoc}
\label{table:1}
\end{table}

@@

Table~\ref{table:2} represents all the ways one can use citations in LaTeX and
expect the generated output.

\begin{table}[htbp]
\centering
\begin{tabular}{| c | c |}
 \hline
 Command & Render \\
 \hline
 \verb|\citet{pandoc}| & \citet{pandoc} \\ \hline
\verb|\citep{pandoc}| & \citep{pandoc} \\ \hline
 \verb|\citet*{pandoc}| & \citet*{pandoc} \\ \hline
\verb|\citep*{pandoc}| & \citep*{pandoc} \\ \hline
 \verb|\citeyear{pandoc}| & \citeyear{pandoc} \\ \hline
\verb|\citeauthor{pandoc}| & \citeauthor{pandoc} \\ \hline
 \verb|\cite{pandoc}| & \cite{pandoc} \\ \hline
\end{tabular}
\caption{Different forms of citation in LaTeX.}
\label{table:2}
\end{table}

\subsubsection{Footnotes}

Footnotes do not work in \verb|tabular| environments in LaTeX but do work in R Markdown tables\footnote{Footnotes in paragraph text work in both LaTeX and R markdown}. Custom footnote numbering works in LaTeX but does not work in R Markdown\footnote[21]{Forever 21 :)}. These features are demonstrated in Table~\ref{table:3}.

\begin{table}[htbp]
\centering
\begin{tabular}{| c | c |}
 \hline
 Command & Render \\
 \hline
 \verb|\acronym{A}\footnote{This works in HTML}| & \acronym{A}\footnote{This works in HTML} \\ \hline
\verb|\R\footnote[21]{HTML shows 2 rather than 21}| & \R\footnote[21]{HTML shows 2 rather than 21}  \\ \hline
\end{tabular}
\caption{Demonstration of footnotes.}
\label{table:3}
\end{table}

\subsubsection{Block quotes}
\begin{quote}
This block quote should justify an example.
\end{quote}

\subsubsection{Links}
Most links work just fine using \verb|\href| and the \verb|\url| command will work flawlessly, as demonstrated in Table ~\ref{table:4}.

\begin{table}[htbp]
\centering
\begin{tabular}{| c | c |}
 \hline
 Command & Render \\
 \hline
 \verb|\href{www.google.com}{Google}| & \href{www.google.com}{Google} \\ \hline
\verb|\url{www.google.com}| & \url{www.google.com}  \\ \hline
\verb|Table \ref{table:3}| & Table \ref{table:3}  \\ \hline
\end{tabular}
\caption{Links}
\label{table:4}
\end{table}

\subsection{Colored text}
Some commands to describe colored text also work during conversion, such as
\verb|\textcolor{blue}{Blue Text}|  \textcolor{blue}{Blue Text}.

\section{Summary}
In summary the \CRANpkg{texor} package alongside pandoc supports:
\begin{itemize}
\item Extracting metadata and putting it together well.
\item Handling links, block quotes, citations and footnotes.
\end{itemize}
